Summary of the things that I learned

### 2023-03-09 summary.tex
Add a summary ofthe paper

>>>>

  \section{Cartesian multicategory}
  Yet another way to think of a cartesian operad is as a one-object cartesian multicategory. A \textbf{cartesian multicategory} is a multicategory with an $ S_n $-action on the hom-sets (in other words: we can permute the arguments of the morphsims) and duplication/diagonal/contraction operations
  \[ \mathrm{Hom}(c_1, \dots, c_k, c_k, \dots, c_n; c) \to \mathrm{Hom}(c_1, \dots, c_k, \dots, c_n; c) \]
  and deletion/projection/weakening operations
  \[ \mathrm{Hom}(c_1, \dots, c_k, \dots, c_n; c) \to \mathrm{Hom}(c_1, \dots, c_{k-1}, c_{k+1}, \dots, c_n; c) \]

  \section{The paper}
  A summary of the results in the paper:
  \begin{enumerate}
    \item A definition of the category of algebraic theories (clones).
    \item A definition of the category of $ T $-algebras (for $ T $ an algebraic theory), the pullback of an algebra, the free algebra, and some properties of these.
    \item A definition of a presheaf (like an algebra, but with a right action instead of a left one) and some properties of this.
    \item A sidenote about the more classical approach to algebra.
    \item A definition for a $ \lambda $-theory and some properties of its constituents.
    \item A definition for an interpretation of the $ \lambda $-calculus in a $ \lambda $-theory, and some properties.
    \item The notion that the algebraic theory $ \Lambda $ of all terms of the $ \lambda $-calculus is the initial $ \lambda $-theory.
    \item The notion that we can add constants to a theory to make sure that it `has enough points'.
    \item A (new) proof that any $ \lambda $-theory is isomorphic to the endomorphism $ \lambda $-theory of some object.
    \item A section that concludes an equivalence between the presheaf categories of a Lawvere theory, a $ \lambda $-theory and the category of retracts.
    \item The definition of $ \Lambda $-algebra and a couple of its properties. In particular, a functor from $ \lambda $-theories to $ \Lambda $-algebras.
    \item An equivalene between $ \Lambda $-algebras and their presheaves.
    \item A characterisation of the function space $ U^U $ for $ U \in PA $ the universal.
    \item An equivalence of categories between the category of $ \Lambda $-algebras and $ \lambda $-theories.
    \item The Fundamental Theorem of the $ \lambda $-calculus: there is an adjoint equivalence between $ \lambda $-theories and $ \Lambda $-algebras.
    \item A remark that this is much harder without the category theoretic framework.
  \end{enumerate}
